Market Simulator

### 2020-08-04 analysis/05_market_simulator.Rmd
Updated with persona beta calculated

---
title: "Market Simulator"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

@@

### Commented out the beta's we don't need right now. We only need the one that contains all the factors.

charity_voluntarism <- readRDS(here('analysis', 'output', 'posterior_draws', 'charity_voluntarism.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

demographics <- readRDS(here('analysis', 'output', 'posterior_draws', 'demographics.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

intercept_centered <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_centered.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

intercept_conjugate <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_conjugate.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Gamma))

intercept_noncentered <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

political_ideology <- readRDS(here('analysis', 'output', 'posterior_draws', 'political_ideology.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

public_affairs <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_affairs.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

public_political <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

public_political_social <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

public_political_social_charity <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

social_views <- readRDS(here('analysis', 'output', 'posterior_draws', 'social_views.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

@@

})

```{r functions}
#### This chunk can be used for writing function to calculate the utilities and what not

@@

Inputs {.sidebar}
-------------------------------------------------------

```{r echo=FALSE}
selectInput("model_choice", 
            label = "Select Model:",
            choices = c("charity_voluntarism",
                        "demographics",
                        "intercept_centered",
                        "intercept_conjugate",
                        "intercept_noncentered",
                        "political_ideology",
                        "public_affairs",
                        "public_political",
                        "public_political_social",
                        "public_political_social_charity",
                        "public_political_social_charity_demo",
                        "social_views"))

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {

    selectInput("charity_importance", 
              label = "Charity Importance:",
              choices = c("0", '1', '2', '3','4','5','6','7'))
  }
})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
  selectInput("trust_in_charity", 
              label = "Charity Trust:",
              choices = c("0", '1', '2', '3','4','5','6','7'))
  }
})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("donation_frequency", 
               label = "Donation Frequency:",
               choices = c('Once a week', 'Once a Month', 'Once every three months', 'Once every six months', 'Once a year', 'Once every few years', 'Never'))
  }
})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("donation_amount", 
               label = "Donation Amount:",
               choices = c("$1-$49", '$50-$99', '$100-$499', '$500-$999','$1,000-$4,999','$5,000-$9,999','$10,000+'))
}})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("volunteer_12", 
               label = "Volunteered in last 12 Months:",
               choices = c("Yes", "No"))
}})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("volunteer_frequency", 
               label = "Volunteer Frequency:",
               choices = c('Once a week', 'Once a Month', 'Once every three months', 'Once every six months', 'Once a year', 'Once every few years', 'Never'))
}})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("personal_activism", 
               label = "Personal Activism:",
               choices = c('Extremely involved', 
               'Very involved', 
               'Moderately involved', 
               'Slightly involved',
               'Never involved'))
}})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("family_activism", 
               label = "Family Activism:",
               choices = c('Extremely involved', 
               'Very involved', 
               'Moderately involved', 
               'Slightly involved',
               'Never involved'))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("religious_member", 
               label = "Church Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("sport_member", 
               label = "Sport or Recreational Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("art_member", 
               label = "Art, Music, or Educational Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("labor_member", 
               label = "Labor Union Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("political_member", 
               label = "Political Party Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("environmental_member", 
               label = "Enviornmental Org. Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("professional_member", 
               label = "Professional Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})
renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("humanitarian_member", 
               label = "Humanitarian Org. Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("consumer_member", 
               label = "Consumer Org. Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("religious_member", 
               label = "Church Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))

  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("other_member", 
               label = "Other Org. Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("national_news", 
               label = "Follow national news:",
               choices = c('Multiple times a day', 
               'Every day', 
               "Once a week",
               "Hardly ever",
               "Never"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("international_news", 
               label = "Follow international news:",
               choices = c('Always',
                           "Sometimes",
                           "Never"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("news_medium", 
               label = "Medium to follow news:",
               choices = c('TV', 
               'Print', 
               "Online",
               "Social Media",
               "Radio",
               "Email newsletters",
               "News app"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("international_news", 
               label = "Follow international news:",
               choices = c('Multiple times a day', 
               'Every day', 
               "Once a week",
               "Hardly ever",
               "Never"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("follow_gov", 
               label = "Follow government & public affairs:",
               choices = c('Most of the time', 
               'Some of the time', 
               "Only now and then",
               "Hardly at all"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("travel_developing", 
               label = "Travel to developing country:",
               choices = c('Yes', 
               'No'))
  }})

renderUI({
  if (input$model_choice %in% c("political_ideology", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("polical_pref", 
               label = "Polical views from liberal to conservative:",
               choices = c('0', 
               '1', 
               "2",
               "3",
               "4",
               "5",
               "6",
               "7"))
  }})

renderUI({
  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("institution_trust", 
               label = "Political institution trust from none to complete:",
               choices = c('0', 
               '1', 
               "2",
               "3",
               "4",
               "5",
               "6",
               "7"))
  }})

renderUI({
  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("others_charitable", 
               label = "People should be more charitable:",
               choices = c('0', 
               '1', 
               "2",
               "3",
               "4",
               "5",
               "6",
               "7"))
  }}) #??

renderUI({
  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("worship_attendance", 
               label = "Worship service attendance:",
               choices = c('Multiple times a week', 
               'Once a week', 
               "Once a month",
               "Once a year",
               "Never"))
  }}) #??

renderUI({
  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("religion_importance", 
               label = "Importance of religion:",
               choices = c('Extremely important',
                           'Very important',
                           'Moderately important',
                           'Slightly important',
                           'Not at all important'))
  }})

renderUI({
  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("religion", 
               label = "Religion:",
               choices = c('Catholic',
                           'Protestant',
                           'Christian Orthodox',
                           'Jewish',
                           'Muslim',
                           'Sikh',
                           'Hindu',
                           'Buddhist',
                           'Atheist',
                           'Other'))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("gender", 
               label = "Gender:",
               choices = c("Male",
                           "Female",
                           "Transgender",
                           "Prefer not to say",
                           "Other"))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("marital_status", 
               label = "Marital Status:",
               choices = c("Married",
                           "Widowed",
                           "Divorced",
                           "Separated",
                           "Never married"))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("education", 
               label = "Education:",
               choices = c("Less than high school",
                           "High school",
                           "Some college",
                           "2 year degree",
                           "4 year degree",
                           "Graduate degree",
                           "Doctorate"))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("income", 
               label = "Income:",
               choices = c('Less than $10,000', 
                           '$10,000 to $19,999',
                           '$20,000 to $29,999',
                           '$30,000 to $39,999',
                           '$40,000 to $49,999',
                           '$50,000 to $59,999',
                           '$60,000 to $69,999',
                           '$70,000 to $79,999',
                           '$80,000 to $89,999',
                           '$90,000 to $99,999',
                           '$100,000 to $149,999',
                           '$150,000 to $199,999',
                           '$200,000 to $299,999',
                           '$300,000 or more'))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("race", 
               label = "Race(s):",
               choices = c('White',
                           'Black or African American','American Indian or Alaska Native','Asian','Native Hawaiian or Pacific Islander', 'Other'), 
               multiple = TRUE)
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("education", 
               label = "Education:",
               choices = c("Less than high school",
                           "High school",
                           "Some college",
                           "2 year degree",
                           "4 year degree",
                           "Graduate degree",
                           "Doctorate"))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("age", 
               label = "Age:",
               choices = c('Under 18',
                           '18 - 24',
                           '25 - 34',
                           '35 - 44',
                           '45 - 54',
                           '55 - 64',
                           '65 - 74',
                           '75 - 84',
                           '85 or older'))
  }})

@@

@@

```{r plot}
renderPlotly({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)

@@

  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  colnames(df) <- c('Value', 'Organization', "Type")

  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Organization)) +
             geom_col() +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none") +
             facet_wrap(~Type)
    )
})
```

Organization Utility
-------------------------------------
## Amnesty International Expected Utility

```{r}
renderValueBox({
  choice = df()
  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  valueBox(ai_exp_util,
           color = "#FFC30B")
})
```

## Greenpeace Expected Utility

```{r}
renderValueBox({
  choice = df()
  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  valueBox(gp_exp_util,
           color = "#3fad48")
})
```

## Oxfam Expected Utility

```{r}
renderValueBox({
  choice = df()
  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  valueBox(ox_exp_util,
           color = "#006633")
})
```

## Redcross Expected Utility

```{r}
renderValueBox({
  choice = df()
  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  valueBox(rc_exp_util,
           color = "#660000")
})
```

Expected Donors {.tabset .tabset-fade}
-------------------------------------
### Amnesty International Expected Donors

```{r echo=FALSE}
renderGauge({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(ai_rate, 
        min = 0, 
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})
```

### Greenpeace Expected Donors

>>>>

---
title: "Market Simulator"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

@@

# Beta's of everything. The only model we care about right now
public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i, j) %>% 
  summarize(theta_mean = mean(Theta)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = theta_mean) %>% 
  select(-i)

# Persona Data from Market Simulator Workbook
persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_config.xlsx"))

@@

})
```

@@

Persona Inputs {.sidebar}
=================================================

## Persona Inputs

```{r sidebar inputs, echo=FALSE}

# selectInput("model_choice", 
#             label = "Select Model:",
#             choices = c("public_political_social_charity_demo"))

selectInput("charity_importance", 
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("trust_in_charity", 
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("donation_frequency", 
         label = "Donation Frequency:",
         choices = c('Once a week', 
                     'Once a Month',
                     'Once every three months',
                     'Once every six months', 
                     'Once a year', 
                     'Once every few years',
                     'Never'))

selectInput("donation_amount", 
         label = "Donation Amount:",
         choices = c("$1-$49", 
                     '$50-$99', 
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("volunteer_12", 
         label = "Volunteered in last 12 Months:",
         choices = c("Yes", "No"))

selectInput("volunteer_frequency", 
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months', 
                     'Once every six months', 
                     'Once a year', 
                     'Once every few years',
                     'Never'))

selectInput("personal_activism", 
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved', 
                     'Moderately involved', 
                     'Slightly involved',
                     'Never involved'))

selectInput("family_activism", 
         label = "Family Activism:",
         choices = c('Extremely involved', 
                     'Very involved', 
                     'Moderately involved', 
                     'Slightly involved',
                     'Never involved'))

selectInput("religious_member", 
         label = "Church Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("sport_member", 
         label = "Sport or Recreational Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("art_member", 
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("labor_member", 
         label = "Labor Union Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("political_member", 
         label = "Political Party Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("environmental_member", 
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("professional_member", 
         label = "Professional Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("humanitarian_member", 
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("consumer_member", 
         label = "Consumer Org. Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("religious_member", 
         label = "Church Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("other_member", 
         label = "Other Org. Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("national_news", 
         label = "Follow national news:",
         choices = c('Multiple times a day', 
                     'Every day', 
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("international_news", 
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("news_medium", 
         label = "Medium to follow news:",
         choices = c('TV', 
                     'Print', 
                     "Online",
                     "Social Media",
                     "Radio",
                     "Email newsletters",
                     "News app"))

selectInput("international_news", 
         label = "Follow international news:",
         choices = c('Multiple times a day', 
                     'Every day', 
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("follow_gov", 
         label = "Follow government & public affairs:",
         choices = c('Most of the time', 
                     'Some of the time', 
                     "Only now and then",
                     "Hardly at all"))

selectInput("travel_developing", 
         label = "Travel to developing country:",
         choices = c('Yes', 'No'))

selectInput("polical_pref", 
         label = "Polical views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("institution_trust", 
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("others_charitable", 
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("worship_attendance", 
         label = "Worship service attendance:",
         choices = c('Multiple times a week', 
                     'Once a week', 
                     "Once a month",
                     "Once a year",
                     "Never"))

selectInput("religion_importance", 
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

selectInput("religion", 
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other'))

selectInput("gender", 
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other"))

selectInput("marital_status", 
         label = "Marital Status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"))

selectInput("education", 
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))

selectInput("income", 
         label = "Income:",
         choices = c('Less than $10,000', 
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

selectInput("race", 
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other'), 
         multiple = TRUE)

selectInput("education", 
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))

selectInput("age", 
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

```{r persona betas}

### Calculating the Persona betas ###

# Persona 1
persona1 <- persona_data[,2]

p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona1)

# Persona 2
persona2 <- persona_data[,3]

p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)

# Persona 3
persona3 <- persona_data[,4]

p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)

<!-- Main page Chart with All Personas -->

Market Share Per Persona
==================================================

### Market Share Per Persona

```{r plot all personas}

renderPlotly({
  choice = df()

    persona1 = p_beta1 # Choose the persona

  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)

  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))

    persona2 = p_beta2 # Choose the persona

  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)

  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))

      persona3 = p_beta3 # Choose the persona

  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)

  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))

  data <- c(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1, ai_rate1, gp_rate1, ox_rate1, rc_rate1, 
            ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2, ai_rate2, gp_rate2, ox_rate2, rc_rate2,
            ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3, ai_rate3, gp_rate3, ox_rate3, rc_rate3)

  df <- as.data.frame(matrix(data, 24, 1))

  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none")
    )
})
```

<!-- Persona 1 page -->

Persona 1 
====================================================

@@

```{r plot person 1}
renderPlotly({
  choice = df()
  persona = p_beta1 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)

@@

  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8)
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Organization)) +
             geom_col() +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none") +
             facet_wrap(~Type)
    )
})
```

Organization Market Share
-------------------------------------
### Amnesty International Market Share

```{r valuebox ai persona 1}
renderValueBox({
  choice = df()

  persona = p_beta1 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  valueBox(ai_rate,
           color = "#FFC30B",
           icon = "fa-percent")
})
```

### Greenpeace Market Share

```{r valuebox gp persona 1}
renderValueBox({
  choice = df()
  persona = p_beta1 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)

  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  valueBox(gp_rate,
           color = "#3fad48",
           icon = "fa-percent")
})
```

### Oxfam Market Share

```{r valuebox ox persona 1}
renderValueBox({
  choice = df()

  persona = p_beta1 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)

  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  valueBox(ox_rate,
           color = "#006633",
           icon = "fa-percent")
})
```

### Redcross Market Share

```{r valuebox rc persona 1}
renderValueBox({
  choice = df()

  persona = p_beta1 # Choose the persona
